### 2018-03-16 paper/3-abstractions.tex
Tiny update to S3

Notice also that, even though \hs{busy} takes a \hs{Task}~\hs{Monad} as its
argument, an application of \hs{busy} to a \hs{Task}~\hs{Functor} or
a \hs{Task}~\hs{Applicative} will typecheck just fine. It feels a bit like
sub-typing, but it is actually just ordinary higher-rank polymorphism at
work~\cite{jones2007practical}.

>>>>

Notice also that, even though \hs{busy} takes a \hs{Task}~\hs{Monad} as its
argument, an application of \hs{busy} to a \hs{Task}~\hs{Functor} or
a \hs{Task}~\hs{Applicative} will typecheck and run just fine. It feels a bit like
sub-typing, but is actually just ordinary higher-rank polymorphism at
work~\cite{jones2007practical}.
